An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-01-30 tex/paper.tex
Making some details more verbose.
This could certainly be expanded.

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{Source code for the Grudger strategy.}
    \label{fig:stewart-code}
\end{figure}

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all strategies against each other. Figure \ref{fig:tournament} shows the
results from the full tournament.

@@

The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
Intuitively this state space uses the initial plays of the opponent to gain some
information about the intentions of it whilst still taking in to account the
recent play.  The actual winning strategy an instance of the this framework for
\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
details of this can be found in \cite{mojones}.

Ideas for this section:
* ZD strategies -- extortionate strategies win well but no ZDs score partiocualrly well,
even ZDGTFT2. With noise the ZD strategies don't win well either.
* TFT, T2FT, TF2T -- no so great but variants with e.g. deadlock breaking, such as OmegaTFT,
fare well
* It's posible to win many matchups as well score highly -- backstabber, doublecrosser,
foolmeonce. These strategies also score well in noisy tournaments
* It's possible to be generally cooperative and still exploit naive strategies effective,
such as LookerUp and MetaHunter
* Long memory strategies are generally better
* Meta strategies fare very well in general, also in noisy tournaments
* Variance of score distributions is surprisingly low

>>>>

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all strategies against each other. Figure~\ref{fig:tournament} shows the
results from the full tournament.

@@

The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
Intuitively this state space uses the initial plays of the opponent to gain some
information about the intentions of it whilst still taking in to account the
recent play.  The actual winning strategy an instance of the this framework for
\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
details of this can be found in \cite{mojones}. In \cite{} experiments are
carried out to evaluate how this particular strategy behaves in environments
other than those in which it was trained\dots

There are various other insights that have been gained from ongoing open
research on the library. These include:

\begin{itemize}
    \item A closer look at zero determinant strategies, showing that
        extortionate strategies obtain a large number of wins \textit{but} do
        not perform particularly well. This is relevant given the findings of
        \cite{Stewart2012} in which zero determinant strategies are shown to be
        able to perform better than a given other strategy. This finding extends
        to noisy tournaments (which are also implemented in the library).
    \item This negative relationship between wins and performance does not
        generalise, there are some strategies that perform well, both in terms
        of matches won and overall performance: Back stabber, Double crosser and
        Fool Me Once. These strategies continue to perform well in noisy
        tournaments.
    \item Strategies like LookerUp and MetaHunter seem to be generally
        cooperative yet still exploit naive strategies. The MetaHunter strategy
        is a particular type of Meta strategy which uses a variety of other
        strategy behaviours to choose a best action. These strategies perform
        very well in general and continue to do so in noisy tournaments.
\end{itemize}

Details for the above can be found at \cite{}.
